Checkpoint 3

### 2020-04-23 Checkpoint3.Rmd
adding data description

```{r, warning=FALSE}
library(dplyr)
library(usmap)
library(maps)
library(ggplot2)
library(tidyverse)
library(ggmap)
library(viridis)
library(rgdal)

@@

@@

```{r}
library(statebins)
plot3<-statebins(state_data = weekbefore, state_col = "state",
                     text_color = "white", value_col = "positive",
                     brewer_pal="Spectral", font_size = 2,breaks =7,
                     legend_title="Week Before",
                 labels = c("0","1-5","5-10","10-20","20-30","30-40","50-100"))

@@

```{r}
pp_check(building_mod)
```

>>>>

```{r, warning=FALSE}
library(dplyr)
library(usmap)
library(maps)
library(ggplot2)
library(tidyverse)
library(ggmap)
library(viridis)
library(rgdal)
library(gridExtra)

@@

`COVID-19 Cases`
The COVID-19 data is provided by The COVID Tracking Project(CTP). All of the  data points come from state/district/territory public health authorities—or, occasionally, from trusted news reporting, official press conferences, or (very occasionally) tweets or Facebook updates from state public health authorities or governors. These numbers are updated daily at 4PM EST. The biggest weakness of this dataset is that there is no standardized methods for states to follow for data collection/report. For example, some states, like Oregon, provide the **full** set of numbers but others provide some or none of these numbers on an ongoing basis. Some crucial states in this outbreak, notably California, Washington, and New York, have not been regularly reporting their total number of people tested. The CTP aims to remedy this uncertainty in states by utilizing other reporting/measuring tools such as: "Directly asking state officials, watching news conferences, gleaning information from trusted news sources, and whatever else it takes to present reliable numbers."

@@

```{r}
library(statebins)
plot3<-statebins(state_data = weekbefore, state_col = "state",
                     text_color = "white", value_col = "positive",
                     brewer_pal="Spectral", font_size = 3,breaks =7,
                     legend_title="Week Before",
                 labels = c("0","1-5","5-10","10-20","20-30","30-40","50-100"))

@@

```{r}
pp_check(building_mod)

# Could build like the sleep study, 50 frames one for each state and how Google Trends changed over time, each state has its own trajectory
# Can we look at each state and how their interest changes over time and if that's related to how many cases are in the state

#What's the trend in interest and how does it depend on cases? 
```
